Competing Bandits: The Perils of Exploration under Competition

### 2018-08-30 paper/competing_bandits.tex
Added some macro.
Removed \asedit{}

%\usepackage[utf8]{inputenc} % allow utf-8 input -- cannot use with AAAI! A.S.
%\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amssymb}
%\usepackage{natbib} % cannot use with AAAI! A.S.

@@

% Alex' macro
\usepackage{xspace}
\newcommand{\OMIT}[1]{}
\newcommand{\xhdr}[1]{\vspace{1mm} \noindent{\bf #1}}
\newcommand{\ie}{{\em i.e.,~\xspace}}
\newcommand{\eg}{{\em e.g.,~\xspace}}
\newcommand{\TS}{\mathrm{TS}}
\newcommand{\DEG}{\mathrm{DEG}}

@@

We ask whether better exploration algorithms are incentivized under competition. We run extensive numerical experiments in a stylized duopoly model in which two firms deploy multi-armed bandit algorithms and compete for myopic users.  We find that duopoly \asedit{and monopoly} tend to favor a primitive ``greedy algorithm" that does not explore, whereas a temporary monopoly (a duopoly with an early entrant) may incentivize better bandit algorithms. Our findings provide new intuition on the ``first-mover advantage" in the digital economy.
\end{abstract}

>>>>

%\usepackage[utf8]{inputenc} % allow utf-8 input -- cannot use with AAAI! A.S.
%\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{natbib} % cannot use with AAAI! A.S.

@@

% Alex' macro
\usepackage{xspace}
\newcommand{\OMIT}[1]{}
\newcommand{\xhdr}[1]{\vspace{1mm} \noindent{\bf #1}}
\newcommand{\ie}{{\em i.e.,~\xspace}}
\newcommand{\eg}{{\em e.g.,~\xspace}}

\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}\xspace}
\newcommand{\TS}{\term{TS}}
\newcommand{\DEG}{\term{DEG}}
\newcommand{\DG}{\term{DG}}
\newcommand{\Beta}{\term{Beta}}

\newcommand{\eps}{\varepsilon}

@@

We ask whether better exploration algorithms are incentivized under competition. We run extensive numerical experiments in a stylized duopoly model in which two firms deploy multi-armed bandit algorithms and compete for myopic users.  We find that duopoly and monopoly tend to favor a primitive ``greedy algorithm" that does not explore, whereas a temporary monopoly (a duopoly with an early entrant) may incentivize better bandit algorithms. Our findings provide new intuition on the ``first-mover advantage" in the digital economy.
\end{abstract}
